%------------------------------------------------------------------------------
\chapter{Submitting your thesis}
\label{sec:submit}\index{submit}
%------------------------------------------------------------------------------

\LaTeX{} file: \url{./guide_submit.tex}\\[1ex]
\noindent
Questions often come up when your thesis is finished and now you have
to print it and submit it. Both the
\foreignquote{ngerman}{Promotionsbüro} and the
\foreignquote{ngerman}{Prüfungsamt} have instructions on what you have
to do, but it is sometimes not clear what this means in terms of the
cover pages offered by this thesis framework.

For the printed version of your thesis, you probably want
\Package{hyperref} links and the table of contents to be black. In
order to do this, you should uncomment the \Macro{hypersetup} command
that is in the thesis main file, just after the
\Macro{usepackage}\texttt{\{thesis\_defs\}}.


%------------------------------------------------------------------------------
\section{PhD thesis}
\label{sec:submit:phd}\index{submit!PhD thesis}\index{PhD}

\input{./guide_phdsubmit}

Appendix~\ref{app:printer} suggests some print shops that can make copies
of your thesis in good enough quality to be accepted by the university
library.


%------------------------------------------------------------------------------
\section{Master/Diplom/Bachelor thesis}
\label{sec:submit:other}\index{submit!MSc thesis}\index{submit!Diplom thesis}\index{submit!BSc thesis}

\subsection{Submission}

\begin{enumerate}
\item Use the file \texttt{Master\_Submit\_Title.tex},\index{MSc}
  \texttt{Diplom\_Submit\_Title.tex}\index{Diplom} or\\
  \texttt{Bachelor\_Title.tex}\index{BSc} for the title pages.
  These are selected by passing one of the options
  \Option{Master}, \Option{Diplom} or \Option{Bachelor}
  to the \Macro{documentclass} or the \Package{ubonn-thesis} package.
  In addition, pass the option \Option{Submit} to 
  to the \Macro{documentclass} or the \Package{ubonn-thesis} package.
\item You have to print and bind three copies of your thesis
  to be submitted to the
  \foreignlanguage{ngerman}{Prüfungsamt}. Nowadays these are usually in
  colour.
\item The first and second referees for your thesis often like to
  have an extra copy of the thesis so that they can make comments when they read
  your thesis -- ask them if they want one. You can usually save the
  institute some money and print these copies in black \& white.
\end{enumerate}

Note that a CV does not have to be included in a Master/Diplom/Bachelor
thesis. This is only needed when you submit a PhD thesis.


\subsection{MSc/Diplom theses for the department library}

\begin{enumerate}
\item Use the file \texttt{Master\_Cover.tex} for the cover and
  \texttt{Master\_Final\_Title.tex}\footnote{Replace Master with Diplom
    as appropriate.} for the title pages.
  These are selected by passing the options \Option{Master, PILibrary}\footnote{%
    or \Option{Diplom, PILibrary}}
  to the \Macro{documentclass} or the \Package{ubonn-thesis} package.
\item There are probably some small corrections you or the referees
  found during the time between submission and the completion of the
  referees' reports and grades. These should be corrected before you
  submit your thesis to the department library.
\item The department
  library\index{department library}\index{library!department} (in the Physikalisches
  Institut) needs 2 printed copies with the file\\
  \texttt{Master\_Cover.tex} as the cover.
  This is selected by passing the options \Option{Master, PILibrary}
  to the \Macro{documentclass} or the \Package{ubonn-thesis} package.
  You have to get
  the \enquote{BONN-IB-YYYY-nnn} number from the librarian. You
  should also include an abstract (in English) on the cover page.
\item This version of the thesis is the one that you usually print if
  you need extra copies for your experiment or research group.
\end{enumerate}


\subsection{BSc theses}

\begin{enumerate}
\item There are probably some small corrections you or the referees
  found during the time between submission and the completion of the
  referees' reports and grades. These should be corrected before you
  print some extra copies of your thesis if your group wants them.
\end{enumerate}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "./thesis_guide"
%%% End:
