%==============================================================================
\chapter{References}
\label{sec:ref}
%==============================================================================

\LaTeX{} file: \url{./guide_refs.tex}\\[1ex]
\noindent
Every thesis should also include a list of references, called the
bibliography in \LaTeX{} terminology. You \enquote{cite} a reference using
the \Macro{cite} command. For example, the book of
Kopka~\cite{kopka04} is my favourite \LaTeX{} book. In general you
should include a non-breaking space, i.e.\ \enquote{\textasciitilde} between
the text and the \Macro{cite} command. In British (UK) English the reference
should come before the punctuation; in American English it comes after
it.\footnote{After some research, it appears to me that the footnote
  number should come after the punctuation, unless the footnote only
  refers to the last word of the phrase or sentence.}

That is the easy part!  Where do you get the references from and how
do you format them? Sources of references are discussed in
Section~\ref{sec:ref:sources}.
There are two options for the formatting. Either you do it by
hand, formatting \Macro{bibitem} entries yourself or you use
\BibTeX. 
More precisely you should use the \Package{biblatex} package.
which is a replacement for traditional \BibTeX.
While \Package{biblatex} and/or \BibTeX\ may appear to be the more complicated option
at the beginning, I strongly recommend that you use it.

In addition, you have to make sure that authors' names are
printed consistently, you include the appropriate collaboration
name, the title is formatted correctly and journals are given
consistent abbreviations. Such topics are discussed in
Section~\ref{sec:ref:bib}.

What about citing a series of articles? Can you
include them in one reference or do you want to keep one article per
reference?
I give some hints on
useful options and settings for \Package{biblatex} below (Section~\ref{sec:ref:bbx}).
If you use traditional \BibTeX\ (which I do not recommend), then you probably have to use the \Package{mcite}
package -- see Section~\ref{sec:ref:mcite}.
Just to take a silly example. The ZEUS collaboration
publications in
2010~\cite{Abramowicz:2010ih,Abramowicz:2010xc,Abramowicz:2010nj} were
not as numerous as in previous years. If you use the standard
\Macro{cite} command and the \Option{unsrt} option or its equivalent,
you get a list of numbers.  In the past one could use the
\Package{mcite} package to make the references nicer, put them all in
one, write the list as [m--n] etc.


%------------------------------------------------------------------------------
\section{Formatting by hand}
\label{sec:ref:bibitem}
%------------------------------------------------------------------------------

Don't! The number of references that you will need will probably grow
fast. It is quite likely that at some point you will decide that they
are not really formatted as you would like them to be. You will almost
certainly add references when you correct your thesis. How do you
make sure they are in the order you want? How do you make sure that
only articles that you actually refer to are in the bibliography?

Suppose you want to use some of the references in your thesis in
conference proceedings or a paper in a journal. Every place where you
publish will have it's own preferred format for the references that
almost certainly will not be the one you chose for your thesis.

If you insist on following this route, consult a book on \LaTeX!


%------------------------------------------------------------------------------
\section{Using \BibTeX\ and \Package{biblatex}}
\label{sec:ref:bibtex}\index{BibTeX@\BibTeX}
%------------------------------------------------------------------------------

I won't pretend that \BibTeX{} is the most user-friendly way of
handling references and there are several things that you have to pay
attention to when you use it for your references.

The two big advantages of \Package{biblatex} and/or \BibTeX{} are: only references that you
actually refer to appear in the bibliography; you can change the
format (consistently) of all articles in the bibliography simply by
changing the style!

The first step is to put your references in one or more \texttt{.bib}
files. For this document they can be found in:
\begin{itemize}
\setlength{\itemsep}{0pt}
\item \url{../guide/guide_refs.bib};
\item \url{../refs/standard_refs-biber.bib} or
  \url{../refs/standard_refs-bibtex.bib};
\item \url{../guide/refs/example_refs-utf8.bib} or
  \url{../guide/refs/example_refs-ascii.bib};
\item \url{../guide/refs/zeus_2009.bib} and
  \url{../guide/refs/zeus_2010.bib}.
\end{itemize}
For each article you specify things like its
title, author, journal etc.

You then include these files into your \LaTeX{} document and
specify which style should be used.
You also have to indicate where you want the bibliography to appear.

At this point you also have to decide which interface to the contents
of the \texttt{.bib} files you want to use. You have a choice of the
original \BibTeX\index{BibTeX@\BibTeX} or the more modern
\Package{biblatex}. If you use \Package{biblatex} you
need something like:
\begin{verbatim}
% Use biblatex for the bibliography
\usepackage[backend=biber,
  style=numeric-comp,sorting=none,block=ragged,firstinits=true]{biblatex}
% \usepackage[backend=bibtex,hyperref=true,
%   style=numeric-comp,sorting=none,block=ragged,firstinits=true]{biblatex}

% Adjustments to output are in this style file:
\usepackage{ubonn-biblatex}

\addbibresource{../mythesis/thesis_refs.bib}
\addbibresource{../refs/standard_refs-biber.bib}
\end{verbatim}
in the document preamble and \Macro{printbibliography} where they
should be printed.
Note that as of version 3.0 of the thesis package,
the \Package{biblatex} command is included in \Package{ubonn-thesis} directly.
To turn it off add the option \Option{biblatex=false}.
\par\noindent
If you use traditional \BibTeX{} you need something like:
\begin{verbatim}
% Use BibTeX for the bibliography
\bibliographystyle{../refs/atlasBibStyleWithTitle.bst}
% \bibliographystyle{unsrt}
\bibliography{../mythesis/thesis_refs,%
  ../refs/standard_refs-bibtex}
\end{verbatim}
at the point where the references should be printed.
Note that \LaTeX{} is sometimes picky about spaces in lists of files,
so you either terminate each line in \Macro{bibliography} with a \% or include all files on one line.

Which should you use? Traditional \BibTeX{} has been around for a long time and is
therefore better known. However, it has many problems when it comes to
sorting, handling more modern sources of information (e.g.\ the web),
etc. 
By now (2015) \Package{biblatex} is rather stable,
so future changes should be minor.
It supports things like online references and enables you to click on references
using the preprint number or DOI to look at a reference. It is also
easier to change the way your references look. I therefore
strongly recommend that you use \Package{biblatex}.

Another serious problem with \BibTeX{} is that it cannot handle
umlauts etc.\ properly. While I have said elsewhere in this document
that you should use UTF-8 encoding so that you can enter ä
etc.\ directly, this does not work with \BibTeX. You can use the
old syntax \verb+\"{a}+.\footnote{%
  In fact you have to write this as \texttt{author = "Br\{\textbackslash"\{u\}\}ning, Oliver"} for it to work properly!
  As an aside, if you look at the \LaTeX\ source code for this footnote,
  it might seem natural to use \Macro{verb} for \texttt{author = ...}.
  However, verbatim does not work in footnotes,
  unless you include other packages such as \Package{fancyvrb}.}
This problem is completely solved if you use
\Package{biblatex} and the \Option{biber} backend.\footnote{%
If for some reason you want to use \Package{biblatex} with the \Option{bibtex8} backend
you have to encode your \texttt{.bib}
files with latin1 instead of UTF-8 if they includes umlauts and use the line:\\
\Macro*{usepackage[backend=bibtex8,bibencoding=latin1]\{biblatex\}}.}
As indicated above, the references in the guide include two versions of the file with some example references:
\begin{itemize}
\setlength{\parskip}{0pt}\setlength{\itemsep}{0pt}
\item \texttt{./guide/refs/examples\_refs-utf8.bib} with UTF-8 encoding;
\item \texttt{./guide/refs/examples\_refs-ascii.bib} without any umlauts.
\end{itemize}
If you try to compile the guide with the wrong file using \BibTeX, you
will get some errors as I have included some umlauts in the example
references.
The thesis skeletons use traditional \BibTeX\ with \TeXLive older than 2011
and \Package{biblatex} with the \Option{biber} backend for newer versions.
See the skeleton \texttt{thesis\_skel/theis\_2009\_skel.tex} for the complete syntax
if you want to use traditional \BibTeX.

That's it? Well almost! First, you will have to make sure that the
entry type that you use corresponds to the type of document that you
are citing. Second, you will probably get some or all of your
references from standard sources such as Spires\footnote{I
  will refer to both as Inspire in this chapter.}, Inspire or CDS, you will have
to change the entries a bit so that they get formatted the way you want.


%------------------------------------------------------------------------------
\section{\BibTeX{} entries}
\label{sec:ref:bib}

In this section I discuss how to format your \BibTeX\ databases,
i.e.\ the \texttt{.bib} files. In the following section I talk about
how you make your references look the way you want them to be in your
thesis.

%------------------------------------------------------------------------------
\subsection{Entry types}
\label{sec:ref:entry}

One question is what entry type you should use for what? I give here
recommendations on what to use for \Package{biblatex}. Some of the entry
types that \Package{biblatex} has are not part of \BibTeX.

\begin{description}
\item[@article] This is easy -- use it for articles\index{article} published in
  journals, e.g.~\cite{Abramowicz:2010ih}.
\item[@book] Just as easy -- use it for books,\index{book} e.g.~\cite{kopka04}.
\item[@proceedings, @inproceedings] The name says it all. Use
  \Option{@inproceedings} for a paper in the proceedings\index{proceedings} and
  \Option{@proceedings} for the whole volume.
\item[@collection] Use it for things such as the ATLAS Technical Design
  Report~\cite{lhc:vol1}\index{report!technical} where the names that you find are the
  editors. Use \Option{@incollection} for a single article in a
  collection.
\item[@report] Use it for conference\index{conference note}\index{note!conference} and
  internal\index{internal note}\index{note!internal} notes. This is
  probably also the best type to use for preprints. You can also use
  \Option{@booklet} or \Option{@online}.
\item[@online] Use it for things that are only available online,
  e.g.~\cite{lshort}.
\item[@thesis] The name says it all.\index{thesis}
  \Option{@phdthesis}\index{PhD thesis}\index{thesis!PhD}  and
  \Option{@mastersthesis}\index{Master thesis}\index{thesis!Master}
  also exist. If you are using \Package{biblatex} you can and should specify
  the thesis type, e.g.\ \texttt{type = \{PhD\}}, see for example a
  PhD thesis~\cite{tlodd:2012}.
\end{description}

\Package{biblatex} also knows about multivolume proceedings etc. See
the manual for more details.

Note that Inspire will always give you a \BibTeX{} entry of type
\Option{@article}, so you should adjust it by hand according to what
the document you refer to really is. CDS tries a bit harder, but you
probably still have to set the entry type by hand.

As indicated above, \Package{biblatex} knows about preprint archives,
online references with a url etc.\ and can format the references so
that you can click on a DOI or arXiv number. Details of how these are
handled are well documented in the manual.  In order to make use of
these abilities you have to modify the Inspire format of the references
a bit so that it is fully compatible with what \Package{biblatex}
expects for preprints etc. More details on this are given below.

What else do you have to be careful about? The first thing to know is
that \Package{biblatex} and \BibTeX{} will try to format your author
names and titles. Thus, if you want the title to remain in exactly the
form you have typed it in include it in \enquote{"\{Title\}"}, i.e.\
both double quotes and braces. If not, collaborations and accelerators
tend to be converted to lowercase, e.g.\ \enquote{lhc} instead of
\enquote{LHC}. If you use an author such as ``ATLAS Collaboration'' it
gets printed as \enquote{A.\ Collaboration}.
If part of a title should not have its case changed enclose it in \{...\},
e.g.\ \enquote{"The \{ATLAS\} Detector"}


%------------------------------------------------------------------------------
\subsection{Entries from Inspire and CDS}
\index{spires}\index{inspire}\index{CDS}
\label{sec:ref:cds}

Things like the LHC Design Report\index{design report} are by default
called \Option{@article} in Inspire~\cite{Bruning:2004ej-inspire} or
\Option{@book} in CDS~\cite{Bruening:782076-CDS}. They are in fact
best declared as \Option{@collection} with the \Option{author} field
replaced by \texttt{editor} and a field indicating the
\texttt{institution} instead of
\texttt{publisher}~\cite{lhc:vol1-final}. You can also add the CDS
link as a \texttt{url} field.

Conference notes,\index{conference note} e.g.\ from ATLAS, are defined
as \Option{@techreport} by CDS~\cite{ATLAS-CONF-2011-008-CDS}. It is
better to just call them \Option{@report}. You should add an author,
usually just \texttt{author = "\{ATLAS
  Collaboration\}",}~\cite{ATLAS-CONF-2011-008-final}. You may also
have to change the month format to avoid error messages. For internal
notes, also call them report and add \texttt{type = {internal report}}
to the entry. Again you could add the CDS link as a \texttt{url}
field. For preprints,\index{preprint} I also think it is best to use
the \Option{@report} entry type.

Books\index{book} need to be changed from \Option{@article} to
\Option{@book} and it is better to give the ISBN in the \texttt{isbn}
field~\cite{Halzen:1984mc-final} rather than the \texttt{reportNumber}
field as given in Inspire~\cite{Halzen:1984mc-inspire}.

Theses\index{thesis} should used the \Option{@thesis} entry type and
then add a \texttt{type} field. Alternatively you can use
\Option{@mastersthesis} or \Option{@phdthesis}.

In all cases you probably have to edit the titles a bit to get
things like $\sqrt{s} = \SI{7}{\TeV}$ printed properly. An open
question is whether you should assume the use of a units package in
the formatting of the title. If you want to make your \texttt{.bib}
files usable by others, it is probably best to do the formatting by
hand.

An example of a typical ATLAS paper as it comes from
Inspire~\cite{Aad:2010ey-inspire} needs a bit of work.  With \TeXLive
2011 the link to DOI and arXiv both work well~\cite{Aad:2010ey-final}.

%\textcolor{red}{Check if this is still true:
%With \TeXLive 2009, it worked on my laptop, but did not work properly
%on ATLAS machines (Ubuntu 10.04) that had version 0.8e of \Package{biblatex}.
%It may be that one can get it to work with a bit of help, but I have
%not tried all possible options.}

% Depending on which\TeXLive 2009 version you actually have, you might
% have to give a bit of help for the arXiv link to
% work%~\cite{Aad:2010ey-tex2009}.


%------------------------------------------------------------------------------
\subsection{More on names}
\label{sec:ref:names}

The best way to format author names so that they appear correctly
whatever \BibTeX{} style you use is \texttt{Surname, Name}. Any other
syntax is likely to get mangled.

What about collaboration names? If you use Inspire as the source of
your \BibTeX{} entries, you will see that it has a field for the
collaboration. This is often, but not always, formatted
correctly. 
However, very few \BibTeX{} styles, and as far as I know no \Package{biblatex} styles, 
pay any attention to this field.
The ones from Inpire listed below will work properly. The
only other reliable alternative I have found is to use the following
syntax:
\begin{verbatim}
@Article{Chekanov:2009qja,
     author    = "{ZEUS Collab.} and Chekanov, S. and others",
\end{verbatim}
which then usually gets formatted as \enquote{ZEUS Collab., S.\ Chekanov et
al.,}.
I went through and changed the references in \texttt{zeus\_2009.bib}
accordingly.


%------------------------------------------------------------------------------
\section{Formatting references}
\label{sec:ref:format}

While \BibTeX{} or \Package{biblatex} format the references for you
from the \texttt{.bib} files, you have to tell them what format you
want!  For a start, you have to choose between an alphabetic and a
numeric scheme for the references. Most journals use a numeric
style. This corresponds to style \Option{unsrt} or a variant thereof
using traditional \BibTeX.  If you use \Package{biblatex} you include the
package with option \Option{numeric-comp} or
\Option{numeric}. \Option{numeric-comp} produces more compact
citations (e.g.\ [1-4,7,9]) than \Option{numeric} (e.g.\
[1,2,3,4,7,9].

For this guide (for a change) I use an alphabetic style:
\Option{alpha} with \BibTeX{} or option \Option{alphabetic} with
\Package{biblatex}. In the thesis skeleton I use a more usual unsorted
numeric style.


%------------------------------------------------------------------------------
\subsection{\Package{biblatex} styles}
\label{sec:ref:bbx}

My experience with \Package{biblatex} has taken off in the last year, 
since I started rewriting the ATLAS \LaTeX\ templates.
The first official stable release of \Package{biblatex} was 19 Oct 2010.
Active and rapid development is ongoing -- there were many updates in 2011.
Some things I recommend below may work a bit differently depending on which version
you have. See Appendix~\ref{sec:app:tex} on how to install a newer
version of \TeXLive if you want a more up-do-date version of \LaTeX.

Looking for numeric styles you can either use the built-in
\Option{numeric} or \Option{numeric-comp}.  The \Option{numeric-comp}
style is used by default in the thesis skeleton. I made a few
adjustments that are included in the file
\texttt{ubonn-biblatex.sty}%
\footnote{In the past (before version 3.0) these files were called
  \texttt{./biblatex/biblatex-num-v2009.sty} and
  \texttt{./biblatex/biblatex-num-v2011.sty}. Which file was used
  by default was steered by the \Macro{texlive} macro which is set in the
  main file.}

You can change some of the things in the style file by passing options to it.
The syntax \Option{articletitle} and \Option{articletitle=true} is equivalent.
Use \Option{articletitle=false} to turn off an option.
The following options exist:

\begin{tabular}{llp{10.0cm}}
  \toprule
  Option & Default & Description \\
  \midrule
  texlive & 2014 & Specify the \TeXLive version.
  You can also use the older command \verb|\newcommand*{\texlive}{2014}|.\\
  articletitle & true & Show the titles of articles and reports;\\
  titlequote & false & Enclose the title in quotes rather than using a slanted font.\\
  boldvol & false & Show the volume in bold face.\\
  showurl & true & Show the URL field.\\
  showdoi & false & Show the DOI separately. Otherwise it is linked from the journal reference.\\
  eprint & true & Show the arXiv entry.\\
  \bottomrule
\end{tabular}

You can fine tune things even more by using hooks that are
available. For example, the way I turn off the URL field is
to include the command:
\begin{verbatim}
\AtEveryBibitem{\clearfield{url}}
\end{verbatim}
in the preamble or in the relevant style file given in the previous
paragraph. It is not clear to me if you also need
\verb+\AtEveryCitekey{\clearfield{url}}+.

A fairly nice-looking style is \Option{ieee}. This is only be
available in recent releases ($\geq 2011$) of \TeXLive. After playing around
a bit with the \Option{ieee} style, I decided it is too new and has
too many settings that depend on having a new version of
\Package{biblatex} for now.

There are slowly more and more \Package{biblatex} styles around, but
not as many as traditional \BibTeX. It is, however, much easier to change things
(usually you can just change an option) with \Package{biblatex} than it
was for traditional \BibTeX, so you can probably start with a standard file and
just make adjustments in your preamble. I have found a number of very
useful hints on how to make changes in
\url{http://tex.stackexchange.com/} -- just search for \Package{biblatex}.

If you include \Package{ubonn-thesis} with the option \Option{astrobib},
the references will be formatted in the style usually used in astrophysics publications.\index{astronomy}\index{astrophysics}
Version 3.0 contains a first version of this option.
A few more tweaks may still be needed. You can use the command
\verb|make astro| instead of \verb|make new| to make a thesis skeleton with the appropriate
options set and the template introduction uses typical citation commands.
The option \Option{astrobib} only works for \TeXLive 2011 and later, i.e.\ with \Package{biblatex}.

If it is available, \Option{biber} is the preferred backend over
\Option{bibtex} or \Option{bibtex8}.
However, the backend is mostly relevant for
sorting, so it probably does not matter which you use if you use an
option that gives the references in the order that they were
cited. \Option{biber} seems to work well with \TeXLive 2012 and later and hence is the default.
For older versions of \TeXLive, a better solution is probably \texttt{make new09}
followed by \texttt{make thesis09} that then uses traditional \BibTeX.\footnote{%
You can still try to use \Package{biblatex} if you want to -- use \texttt{make new} to create a new skeleton --
as \texttt{ubonn-thesis} switches to \Option{bibtex} automatically for \TeXLive
versions earlier than 2011.
Compile the thesis with \texttt{make thesis09} though.
If you want to set the backend yourself, use the option \Option{backend}.
Set the encoding with the option \Option{bibencoding} if necessary.}

If you want to find out where your references are actually cited, you
can include the option \Option{backref=true}.

If you get an error such as:
{\scriptsize
\begin{verbatim}
biber     thesis_guide
data source /tmp/par-62726f636b/cache-ab06f20732bfab23dfa35f56998ad4edca61bee1//inc/lib/Biber/LaTeX/recode_data.xml not found in .
Compilation failed in require at Biber/Utils.pm line 21.
\end{verbatim}
}
\noindent
then you should delete the directory \texttt{/tmp/par-...} and try to
run again. The directory name depends on the operating system you are using.
Use the command \verb|biber --cache| to find out where it is.
If you are adventurous, the command \verb|rm -rf `biber --cache`| will do it all for you!

%------------------------------------------------------------------------------
\subsection{Traditional \BibTeX{} styles}
\label{sec:ref:bst}

If you use references directly from Spires or Inspire, then it is
probably best to use one of the style files that is compatible with
their format. A list can be found on
\url{http://www.slac.stanford.edu/spires/hep/refs/bibstyles.shtml}. I
have used \Option{utphys} a few times and it works OK. I see that
there are also style files available there for common HEP journals,
which could save quite a bit of work. The big advantage of
\Option{utphys} is that it also knows about the arXiv and preprints.

The equivalent of \Package{biblatex}'s \Option{ieee} style in \BibTeX\ is
\Option{ieeetr}. It also knows about arXiv and preprints. However, it
does not know about collaborations.

There are also standard ATLAS style files that work fairly well:
\texttt{atlasBibStyleWithTitle.bst} and \texttt{atlasBibStyleWoTitle.bst}
These are included in the \texttt{refs} directory.


%------------------------------------------------------------------------------
\section{Sources for references}
\label{sec:ref:sources}
%------------------------------------------------------------------------------

The ZEUS collaboration kept a reasonably up-to-date list of ZEUS and
H1 publications (as well as some others) in \BibTeX{} format. ATLAS
also keeps such a list and I assume that other collaborations keep
similar lists.

Within experimental high energy physics the standard way to get a
reference is to use Inspire
(\url{http://inspirehep.net}).\footnote{This has now replaced Spires
(\url{http://www.slac.stanford.edu/spires/}).
One problem with Spires was that it was very slow and regularly
timed out when you perform searches.} You can get the appropriate
Inspire entry by using the Inspire search engine. Alternatively if you
know the arXiv preprint number you can go from its entry to Inspire
directly.

To get the ZEUS references I used above I first tried the following
command in Inspire:
\begin{verbatim}
find exp zeus and date 2009
\end{verbatim}
This does not really give you the references you expect though! It
seems much more reliable to use an author name so I used:
\begin{verbatim}
find a chekanov and date 2009
\end{verbatim}
and then selecting \BibTeX{} format, saving the resulting page in a file
and removing the \texttt{<pre>} and \texttt{</pre>} entries between
references. This worked better, even though I got a whole load of
ATLAS papers as well.

If you then try to use the references, you get complaints that
something is not in math mode. You have to go through by hand and
change things such as \verb+Q^2+ to \verb+$Q^{2}$+.


%------------------------------------------------------------------------------
\section{Common wishes}
\label{sec:ref:tips}
%------------------------------------------------------------------------------

It is possible that you would like to combine several articles into a
single reference. The \Package{mcite} package was designed to do this,
but is not compatible with \Package{biblatex} and
\Package{hyperref}. \Package{biblatex} has another solution that it
calls sets.

In \texttt{standard\_refs-biber.bib} and
\texttt{standard\_refs-bibtex.bib} I have put in the three standard
references for the Standard Model~\cite{gsw}. They are combined by
using \Option{@Set}\index{biblatex!Set option@"@Set option} and the relevant
keys. If you use a recent version of \texttt{biber} (\TeXLive 2012 and later)
this is all you have to do.  If, however, you are using \TeXLive
2011 or earlier with \Package{biblatex}, and therefore the \texttt{bibtex} or \texttt{bibtex8} backend, the
\texttt{crossref} field must contain the same key as the first one in
\texttt{entryset}.

One thing you should always do is include all references in a single
\Macro{cite}. e.g.\ there were quite a few ZEUS publications in
2009~\cite{Chekanov:2009qja,Chekanov:2009zz,Chekanov:2009tu} is better
than~\cite{Chekanov:2009qja}\cite{Chekanov:2009zz}\cite{Chekanov:2009tu}.
If you want to get a list of references printed in the form \enquote{[m--n]},
then with \Package{biblatex} you should use the style
\Option{numeric-comp}. In 2009 there were many papers published by the
ZEUS
collaboration~\cite{Chekanov:2009qja,Chekanov:2009zz,Chekanov:2009tu}
as well as several articles from both the H1 and ZEUS
collaborations\cite{Chekanov:2009wt,Aaron:2009wg}. See
Section~\ref{sec:ref:mcite} on how to do this with \BibTeX.

In some areas, it is more common to give a bibliography per chapter,
rather than collecting all references at the end of the thesis.
This is straightforward to achieve with \Package{biblatex}.
Simply add the option \Option{refsection=chapter} when you include \Package{biblatex}.
This and more can be done by passing the option \Option{astrobib} to \Package{ubonn-thesis}.
In addition you have give the command\\
\Macro{printbibliography[heading=subbibliography]} at the end of each chapter.
The thesis skeleton contains such commands commented out.
The command \texttt{make astro} uses a skeleton with a bilbiogrpaphy per chapter.
The option \Option{astrobib} also sets things up so that the \Package{natbib} citation
commands \Macro{citep}, \Macro{citet} and \Macro{citealt} can be used,
so that the citation appears as expected for astronomy publications.

You are nearing the end of your thesis and have to properly format all
the references that you have. However, they are spread over several
files and these files also contain many references that you do not use
or want to correct. How best to proceed?
\begin{verbatim}
bibtool -x mythesis.aux -o refs.bib
\end{verbatim}\index{bibtool}
will extract the entries that you use and in future you can use and
correct \texttt{refs.bib}, which only contains the references that you
actually cite.\footnote{%
I got this tip from
\url{http://tex.stackexchange.com/questions/417/how-to-split-all-bibtex-referenced-entries-from-a-big-bibtex-database-to-a-copy}.
Do not forget to change \texttt{mythesis.tex} to use
\texttt{refs.bib} instead of the previous sources.}


%------------------------------------------------------------------------------
\section{Using \Package{mcite}}
\label{sec:ref:mcite}
%------------------------------------------------------------------------------

As mentioned above, the \Package{mcite} package used to be a good way
of combining several articles into a single references and also
getting them to be printed out in the form \enquote{[m--n]}, rather
than \enquote{[l,m,n]} or \enquote{[l],[m],[n]}. How do you achieve
this?  Just put all the articles in a single \Macro{cite} and prefix
those that should be lumped together with a \enquote{*}, e.g.\
\verb+\cite{Chekanov:2009wt,*Aaron:2009wg,*Aaron:2009sma}+.  The
problem is that this package does not appear to be compatible with the
\Package{hyperref} package, so you have to choose between the
two. Given the ability that the \Package{hyperref} package offers to
jump directly to sections, equations, references referred to in a
document, I guess most of you will go with \Package{hyperref} rather
than \Package{mcite}.

As mentioned above the \Package{biblatex} package offers a
more modern alternative and different ways of achieving the same
results! It is also not compatible with \Package{mcite}.

A modified version \Package{mcite} is used by ZEUS in its LaTeX4ZEUS
environment, which is why I include a short description here.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "./thesis_guide"
%%% End:
